---
title: "HW4 Rmarkdown and Litterfall Module Synthesis"
author: "Courtney Lopez"
date: "2/22/2018"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Delete this text, and add 3-4 paragraphs of introduction. This should include background on the NEON project, the sets of sites you are comparing, and the focal site you select for focused temporal analysis.

# Methods

Describe briefly where the data came from, including how they were collected in the field (information is in the pdf file in the data folder), and how you are analyzing them (e.g. using R to visualize the results and an ANOVA to test for significant differences).

# Results

```{r}
# read in litterfall data
litterfall_data <- read.csv("data/ltr_massdata.csv",
                            header = TRUE)
```

```{r}
# subset 
```

Add a number of code chunks in the Results section. These should read in, subset and plot the data as needed (no need to save it to pdf, since it will be put into the rendered docx when you click 'knit'), and, for any boxplots you make, run an appropriate statistical test on your dataset.

# Discussion

Discuss the results you found. In the context of what you know about the site/sites and the predominant types of vegatation in those locations. What do the results indicate about the flow of C and N from the autotrophic biota and into the soil in comparison to what occurs at other sites and over time?
